Flowchart of Current Algorithm

### 2008-10-23 docs/flowchart/paper.tex
equation cleanup only

\item {\bf Advect Base}$[\rho_0^{\inp}, (\rho h)_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp}] \rightarrow (\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp})$ \\
is the process by which we update the base state through $\dt$ in
time \MarginPar{we need a separate section for spherical} given the
radial velocity $w_0^{\inp}.$ The base state arrays are all
one-dimensional in the radial coordinate; we think of the base state
quantities as defined at cell centers, with $w_0$ and $\beta_0$
defined halfway in-between.

@@

\item For the enthalpy update, we discretize
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} = -\nabla\cdot\left[(\rho h)_0w_0\er\right] + \psi \enskip ,
\end{equation}
to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r}
\left [ \left( {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] 
+ \dt\psi_j^{\inp} \enskip ,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in 
the forcing for the interface state calculation, but is used in the update.

@@

\item {\bf Correct Base}
$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow (\rho_0^{\outp})$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

@@

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g 
\enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh}$ and the volume discrepancy correction with $f=0.3$,
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}}
\left[ \psi^{\nmh} - 
f \left(\frac{p_0^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n} \right)\right]
\enskip .
\end{equation}

@@

The procedure to construct $\uadvone$ is described in detail in Appendix B of paper III.
We note that  $\uadvone$ satisfies the discrete versions of 
\begin{equation}
\int_{\Omega_H} \ut \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}
(paper III; eq.~[21])
and
\begin{equation}
\nablab \cdotb (\beta_0 \ut )  = \beta_0 \left(S - \Sbar \right )\enskip ,
\label{eq:tildeconstraint}
\end{equation}
(paper III; eq.~[39]).  The discretization with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left(S^{\nph,\star} - \overline{S}^{\nph,\star}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left(\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right) \enskip .
\end{equation}

@@

\item
Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left( \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) 
\right) \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}

@@

\item {\bf Advect Base}$(\rhozero^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph,\star}, \psi^{\nmh}) \rightarrow $
$(\rho_0^{(2),\star}, (\rho h)_0^{(2),\star}, \rho_0^{\nph,\star,{\rm pred}}, p_0^{n+1,\star}).$

@@

\begin{equation}
\rho^{(1),\nph,\star} = 
\rho^{'(1),\nph,\star} + \left(\frac{\rho_0^n + \rho_0^{(2),\star}}{2}\right) \enskip ,
\end{equation}

  \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$
  without explicitly including the reaction terms,
\begin{equation}
(\rho X_k)^{(2),\star} = (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip ,
\end{equation}
\begin{equation}
\rho^{(2),\star} = \sum_k (\rho X_k)^{(2),\star} \enskip ,
\end{equation}
\begin{equation}
X_k^{(2),\star} = (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{equation}

@@

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ (\uadvone \cdotb \er + w_0^{\nph,\star}) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph,\star} = 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip ,
\end{equation}
\begin{equation}
 \psi_j^{\nph,\star} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{equation}

@@

  \item Compute the enthalpy edge state, $(\rho h)^{(1),\nph,\star},$
    for the conservative update of $(\rho h).$  Here we predict $(\rho
    h)'$ to the edges to obtain $(\rho h)^{'(1),\nph,\star}$, 
    using a second-order Taylor expansion in space
    and time, as described in paper II, Appendix A, using $\V =
    \uadvone+w_0^{\nph,\star} \er$.  We do not include the reaction
    terms in the enthalpy prediction, since we accounted for them
    already in {\bf React State}.  We use the base state enthalpy,
    $(\rho h)_0$, to convert this to an edge state for $(\rho h)$,
    \MarginPar{in these notes we currently assume pred type 1, $(\rho h)'$}
\begin{equation}
(\rho h)^{(1),\nph,\star} = 
(\rho h)^{'(1),\nph,\star} + \left(\frac{(\rho h)_0^n + (\rho h)_0^{(2),\star}}{2}\right)
\enskip .
\end{equation}

  \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2'),\star}$ without
  explicitly including the reaction terms,
  \begin{eqnarray}
  (\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab
      \cdotb \left( (\uadvone+w_0^{\nph,\star} \er) (\rho
      h)^{(1),\nph,\star} \right) \right] \nonumber \\ && + \dt \;
    \left(\uadvone \cdotb \er\right) \left(\frac{\partial
      p_0}{\partial r} \right)^{n} + \dt \; \psi^{\nph,*} \enskip ,
  \end{eqnarray}
  \MarginPar{we should also show the update in the case that $(\rho h)'$ is the flux}
  \end{enumerate}

\item {\bf Correct Base}
$[\rho_0^{(2),\star}, (\nabla\cdot\etarho\er)^{\nph,*}] \rightarrow (\rho_0^{n+1,\star})$.

@@

\item Define
\begin{eqnarray}
 \gammabar^{n+1,\star}    &=& {\rm{\bf Avg}} \left( \Gamma_1(\rho^{n+1,\star}, p_0^{n+1,\star}, 
                                                      X_k^{n+1,\star}) \right) \enskip , \\
 {\beta   }_0^{n+1,\star}    &=& \beta   \left(\rho_0^{n+1,\star}, p_0^{n+1,\star}, \gammabar^{n+1,\star}\right) \enskip .
\end{eqnarray}

@@

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}) with the 
volume discrepancy correction,
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = 
\overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left[ \psi^{\nph,\star} - f \left(\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right)\right]
\enskip ,
\end{equation}
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}
\end{equation}
\begin{equation}
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}
\end{equation}
\begin{equation}
\overline{p(\rho,h,X_k)^{\nph,\star}} = 
\frac{\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}}{2}
\end{equation}

@@

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=& 
\beta_0^{\nph,\star} \left(S^{\nph} - \overline{S}^{\nph}\right) \nonumber \\
&& + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left(\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right)
\enskip , \nonumber \\
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\item {\bf Advect Base}$(\rho_0^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph}, \psi^{\nph,\star} ) \rightarrow $
$(\rho_0^{(2)}, (\rho h)_0^{(2)}, \rho_0^{\nph,{\rm pred}}, p_0^{n+1}).$

@@

\begin{equation}
\rho^{(1),\nph} = \rho^{'(1),\nph} + \left(\frac{\rho_0^n + \rho_0^{(2)}}{2}\right)\enskip ,
\end{equation}

    \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2)}$
      without explicitly including the reaction terms,
\begin{equation}
(\rho X_k)^{(2)} = (\rho X_k)^{(1)} 
- \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho X_k)^{(1),\nph} \right) \right]  \enskip ,
\end{equation}
\begin{equation}
\rho^{(2)} = \sum_k (\rho X_k)^{(2)} \enskip ,
\end{equation}
\begin{equation}
X_k^{(2)} = (\rho X_k)^{(2)} / \rho^{(2)}
\end{equation}

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\uadvtwo \cdotb \er + w_0^{\nph}) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph} = \frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
\end{equation}
\begin{equation}
 \psi_j^{\nph} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{equation}

@@

  \item Compute the enthalpy edge state, $(\rho h)^{(1),\nph}$, for
    the conservative update of $(\rho h)$. Here we predict $(\rho h)'$
    to the edges to obtain $(\rho h)^{'(1),\nph}$, 
    using a second-order Taylor expansion in space and
    time, as described in paper II, Appendix A, using $\V =
    \uadvtwo+w_0^{\nph} \er$.  Again, we do not include the reaction
    terms in the enthalpy prediction since we accounted for them
    already in {\bf React State}. We use the base state enthalpy,
    $(\rho h)_0$, to convert these to edge states for $(\rho h)$,
\begin{equation}
(\rho h)^{(1),\nph} = 
(\rho h)^{'(1),\nph} + \left(\frac{(\rho h)_0^n + (\rho h)_0^{(2)}}{2}\right) \enskip .
\end{equation}

   \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ without
     explicitly including the reaction terms,
\begin{eqnarray}
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho h)^{(1),\nph} \right) \right] \nonumber \\
&& + \frac{\dt}{2} \; \left(\uadvtwo \cdotb \er\right)
\left [ \left(\frac{\partial p_0}{\partial r} \right)^{n}
      + \left(\frac{\partial p_0}{\partial r} \right)^{n+1}  \right ] 
+ \dt \; \psi^{\nph} \enskip ,
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2)}, (\nabla\cdot\etarho\er)^{\nph}] \rightarrow (\rho_0^{n+1})$

@@

\item Define
\begin{eqnarray}
 \gammabar^{n+1}    &=& {\rm{\bf Avg}}\left(\Gamma_1(\rho^{n+1}, p_0^{n+1}, {X_k}^{n+1}) \right) \enskip , \\ 
 {\beta   }_0^{n+1}    &=& \beta   \left(\rho_0^{n+1}, p_0^{n+1},   \gammabar^{n+1}\right) \enskip .
\end{eqnarray}

@@

The velocity update happens analogously to paper II, using $S^{n+1}$ from step 10.
We update the velocity field $\ut^n$ to $\ut^{n+1,\star}$ by discretizing
\begin{equation}
\frac{\partial\ut}{\partial t} = - \ut \cdotb \nablab \ut - w_0 \frac{\partial \ut}{\partial r}
                                 - \left(\ut \cdotb \er\right) \frac{\partial w_0}{\partial r} \er
                                 - \frac{1}{\rho} \nablab\pi
                                 + \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \er
                                 - \frac{(\rho-\rhozero)}{\rho} \; g \; \er  \label{eq:utildeupd}  \enskip\
 ,
\end{equation}
(paper III; eq.~[37]) as 
\begin{eqnarray}
\ut^{n+1,\star} &=& \ut^n - \dt \;
 \left[\left((\uadvtwo+ w_0^{\nph} \er) \cdotb \nablab\right) \ut \right]^\nph
      - \dt \; \left(\uadvtwo \cdotb \er\right)  \left(\frac{\partial w_0^{\nph}}{\partial r} \right) \er \nonumber \\
   &&   + \dt \left[ - \frac{1}{\rho^\nph} {\mathbf{G}} \pi^\nmh
        + \frac{1}{\rho_0} {\mathbf{G}} \pizerotwo
        - \frac{(\rho^\nph-\rhozero^\nph)}{\rho^\nph} g \er \right] \enskip ,
\end{eqnarray}
where $\rho^\nph = ( \rho^n + \rho^{n+1} )/2$
and $\mathbf{G}$ approximates a cell-centered gradient from nodal data. 
The construction of $\left[((\uadvtwo+ w_0^{\nph} \er) \cdotb \nablab) \ut \right]^\nph$
is described in paper II, Appendix A, with $\V = \uadvtwo+w_0^{\nph} \er$ and~$s$ set to each
component of $\ut^n$ individually.

>>>>

\item {\bf Advect Base}$[\rho_0^{\inp}, (\rho h)_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp}] \rightarrow [\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp}]$ \\
is the process by which we update the base state through $\dt$ in
time \MarginPar{we need a separate section for spherical} given the
radial velocity $w_0^{\inp}.$ The base state arrays are all
one-dimensional in the radial coordinate; we think of the base state
quantities as defined at cell centers, with $w_0$ and $\beta_0$
defined halfway in-between.

@@

\item For the enthalpy update, we discretize
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} = -\nabla\cdot\left[(\rho h)_0w_0\er\right] + \psi \enskip ,
\end{equation}
to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r}
\left\{ \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j+\myhalf} -  
         \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j-\myhalf} \right\}
+ \dt\psi_j^{\inp} \enskip ,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in 
the forcing for the interface state calculation, but is used in the update.

@@

\item {\bf Correct Base}
$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

@@

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g 
\enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh}$ and the volume discrepancy correction with $f=0.3$,
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}}
\left\{ \psi^{\nmh} - 
f \left[\frac{p_0^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n} \right]\right\}
\enskip .
\end{equation}

@@

The procedure to construct $\uadvone$ is described in detail in Appendix B of paper III.
We note that  $\uadvone$ satisfies the discrete versions of 
\begin{equation}
\int_{\Omega_H} \ut \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}
(paper III; eq.~[21])
and
\begin{equation}
\nablab \cdotb (\beta_0 \ut )  = \beta_0 \left(S - \Sbar \right )\enskip ,
\label{eq:tildeconstraint}
\end{equation}
(paper III; eq.~[39]).  The discretization with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left(S^{\nph,\star} - \overline{S}^{\nph,\star}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right] \enskip .
\end{equation}

@@

\item
Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}

@@

\item {\bf Advect Base}$[\rhozero^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph,\star}, \psi^{\nmh}] \rightarrow $
$[\rho_0^{(2),\star}, (\rho h)_0^{(2),\star}, \rho_0^{\nph,\star,{\rm pred}}, p_0^{n+1,\star}].$

@@

\begin{equation}
\rho^{(1),\nph,\star} = 
\rho^{'(1),\nph,\star} + \frac{\rho_0^n + \rho_0^{(2),\star}}{2} \enskip ,
\end{equation}

  \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$
  without explicitly including the reaction terms,
\begin{equation}
(\rho X_k)^{(2),\star} = (\rho X_k)^{(1)} 
 - \dt \; \left\{ \nablab \cdotb \left[ \left(\uadvone+w_0^{\nph,\star} \er\right)  
  (\rho X_k)^{(1),\nph,\star} \right] \right\} \enskip ,
\end{equation}
\begin{equation}
\rho^{(2),\star} = \sum_k (\rho X_k)^{(2),\star} \enskip ,
\end{equation}
\begin{equation}
X_k^{(2),\star} = (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{equation}

@@

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ \left(\uadvone \cdotb \er + w_0^{\nph,\star}\right) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph,\star} = 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip ,
\end{equation}
\begin{equation}
 \psi_j^{\nph,\star} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{equation}

@@

  \item Compute the enthalpy edge state, $(\rho h)^{(1),\nph,\star},$
    for the conservative update of $(\rho h).$  Here we predict $(\rho
    h)'$ to the edges to obtain $(\rho h)^{'(1),\nph,\star}$, 
    using a second-order Taylor expansion in space
    and time, as described in paper II, Appendix A, using $\V =
    \uadvone+w_0^{\nph,\star} \er$.  We do not include the reaction
    terms in the enthalpy prediction, since we accounted for them
    already in {\bf React State}.  We use the base state enthalpy,
    $(\rho h)_0$, to convert this to an edge state for $(\rho h)$,
    \MarginPar{in these notes we currently assume pred type 1, $(\rho h)'$}
\begin{equation}
(\rho h)^{(1),\nph,\star} = 
(\rho h)^{'(1),\nph,\star} + \frac{(\rho h)_0^n + (\rho h)_0^{(2),\star}}{2}
\enskip .
\end{equation}

  \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2'),\star}$ without
  explicitly including the reaction terms,
  \begin{eqnarray}
  (\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab
      \cdotb \left[ \left(\uadvone+w_0^{\nph,\star} \er\right) (\rho
      h)^{(1),\nph,\star} \right] \right\} \nonumber \\ && + \dt \;
    \left(\uadvone \cdotb \er\right) \left(\frac{\partial
      p_0}{\partial r} \right)^{n} + \dt \; \psi^{\nph,*} \enskip ,
  \end{eqnarray}
  \MarginPar{we should also show the update in the case that $(\rho h)'$ is the flux}
  \end{enumerate}

\item {\bf Correct Base}
$[\rho_0^{(2),\star}, (\nabla\cdot\etarho\er)^{\nph,*}] \rightarrow [\rho_0^{n+1,\star}]$.

@@

\item Define
\begin{eqnarray}
 \gammabar^{n+1,\star}    &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{n+1,\star}, p_0^{n+1,\star}, 
                                                      X_k^{n+1,\star}) \right] \enskip , \\
 {\beta   }_0^{n+1,\star}    &=& \beta   \left(\rho_0^{n+1,\star}, p_0^{n+1,\star}, \gammabar^{n+1,\star}\right) \enskip .
\end{eqnarray}

@@

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}) with the 
volume discrepancy correction,
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = 
\overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left\{ \psi^{\nph,\star} - f \left[\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\}
\enskip ,
\end{equation}
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}
\end{equation}
\begin{equation}
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}
\end{equation}
\begin{equation}
\overline{p(\rho,h,X_k)^{\nph,\star}} = 
\frac{\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}}{2}
\end{equation}

@@

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=& 
\beta_0^{\nph,\star} \left(S^{\nph} - \overline{S}^{\nph}\right) \nonumber \\
&& + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]
\enskip , \nonumber \\
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\item {\bf Advect Base}$(\rho_0^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph}, \psi^{\nph,\star} ) \rightarrow $
$[\rho_0^{(2)}, (\rho h)_0^{(2)}, \rho_0^{\nph,{\rm pred}}, p_0^{n+1}].$

@@

\begin{equation}
\rho^{(1),\nph} = \rho^{'(1),\nph} + \frac{\rho_0^n + \rho_0^{(2)}}{2}\enskip ,
\end{equation}

    \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2)}$
      without explicitly including the reaction terms,
\begin{equation}
(\rho X_k)^{(2)} = (\rho X_k)^{(1)} 
- \dt \; \left\{ \nablab \cdotb \left[\left(\uadvtwo+w_0^{\nph} \er\right)  
(\rho X_k)^{(1),\nph} \right] \right\}  \enskip ,
\end{equation}
\begin{equation}
\rho^{(2)} = \sum_k (\rho X_k)^{(2)} \enskip ,
\end{equation}
\begin{equation}
X_k^{(2)} = (\rho X_k)^{(2)} / \rho^{(2)}
\end{equation}

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\left(\uadvtwo \cdotb \er + w_0^{\nph}\right) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph} = \frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
\end{equation}
\begin{equation}
 \psi_j^{\nph} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{equation}

@@

  \item Compute the enthalpy edge state, $(\rho h)^{(1),\nph}$, for
    the conservative update of $(\rho h)$. Here we predict $(\rho h)'$
    to the edges to obtain $(\rho h)^{'(1),\nph}$, 
    using a second-order Taylor expansion in space and
    time, as described in paper II, Appendix A, using $\V =
    \uadvtwo+w_0^{\nph} \er$.  Again, we do not include the reaction
    terms in the enthalpy prediction since we accounted for them
    already in {\bf React State}. We use the base state enthalpy,
    $(\rho h)_0$, to convert these to edge states for $(\rho h)$,
\begin{equation}
(\rho h)^{(1),\nph} = 
(\rho h)^{'(1),\nph} + \frac{(\rho h)_0^n + (\rho h)_0^{(2)}}{2} \enskip .
\end{equation}

   \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ without
     explicitly including the reaction terms,
\begin{eqnarray}
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab \cdotb \left[ \left(\uadvtwo+w_0^{\nph} \er\right)  
(\rho h)^{(1),\nph} \right] \right\} \nonumber \\
&& + \frac{\dt}{2} \; \left(\uadvtwo \cdotb \er\right)
\left [ \left(\frac{\partial p_0}{\partial r} \right)^{n}
      + \left(\frac{\partial p_0}{\partial r} \right)^{n+1}  \right ] 
+ \dt \; \psi^{\nph} \enskip ,
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2)}, (\nabla\cdot\etarho\er)^{\nph}] \rightarrow [\rho_0^{n+1}]$

@@

\item Define
\begin{eqnarray}
 \gammabar^{n+1}    &=& {\rm{\bf Avg}}\left[\Gamma_1(\rho^{n+1}, p_0^{n+1}, {X_k}^{n+1}) \right] \enskip , \\ 
 {\beta   }_0^{n+1}    &=& \beta   \left(\rho_0^{n+1}, p_0^{n+1},   \gammabar^{n+1}\right) \enskip .
\end{eqnarray}

@@

The velocity update happens analogously to paper II, using $S^{n+1}$ from step 10.
We update the velocity field $\ut^n$ to $\ut^{n+1,\star}$ by discretizing
\begin{equation}
\frac{\partial\ut}{\partial t} = - \ut \cdotb \nablab \ut - w_0 \frac{\partial \ut}{\partial r}
                                 - \left(\ut \cdotb \er\right) \frac{\partial w_0}{\partial r} \er
                                 - \frac{1}{\rho} \nablab\pi
                                 + \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \er
                                 - \frac{(\rho-\rhozero)}{\rho} \; g \; \er  \label{eq:utildeupd}  \enskip\
 ,
\end{equation}
(paper III; eq.~[37]) as 
\begin{eqnarray}
\ut^{n+1,\star} &=& \ut^n - \dt \;
 \left[\left(\uadvtwo+ w_0^{\nph} \er\right) \cdotb \nablab \ut \right]^\nph
      - \dt \; \left(\uadvtwo \cdotb \er\right)  \left(\frac{\partial w_0^{\nph}}{\partial r} \right) \er \nonumber \\
   &&   + \dt \left[ - \frac{1}{\rho^\nph} {\mathbf{G}} \pi^\nmh
        + \frac{1}{\rho_0} {\mathbf{G}} \pizerotwo
        - \frac{(\rho^\nph-\rhozero^\nph)}{\rho^\nph} g \er \right] \enskip ,
\end{eqnarray}
where $\rho^\nph = ( \rho^n + \rho^{n+1} )/2$
and $\mathbf{G}$ approximates a cell-centered gradient from nodal data. 
The construction of $[(\uadvtwo+ w_0^{\nph} \er \cdotb \nablab) \ut ]^\nph$
is described in paper II, Appendix A, with $\V = \uadvtwo+w_0^{\nph} \er$ and~$s$ set to each
component of $\ut^n$ individually.
